\ttitle

### 2014-01-10 main.tex
Added plots for chapter 6
Put captions above tables

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{http://rvlasveld.github.io}{\authornames}, \href{http://www.uu.nl}\textsc{UU} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{flushright} \large
\emph{Supervisors:} \\
\href{http://www.cs.uu.nl/staff/gv.html}{Dr. G.A.W. \textsc{Vreeswijk}, \href{http://www.uu.nl}\textsc{UU}}  \\ % Supervisor name - remove the \href bracket to remove the link
\href{http://www.annevanrossum.com}{Anne \textsc{van Rossum}, \href{http://www.almende.com}\textsc{Almende B.V.}} % Supervisor name - remove the \href bracket to remove the link
\end{flushright}
\end{minipage}\\[3cm]

@@

The acknowledgements and the people to thank go here, don't forget to include your project advisor\ldots
}
\clearpage % Start a new page

>>>>

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{http://rvlasveld.github.io}{\authornames}, \href{http://www.uu.nl}{\textsc{UU}} % Author name - remove the \href bracket to remove the link
\end{flushleft}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\begin{flushright} \large
\emph{Supervisors:} \\
\href{http://www.cs.uu.nl/staff/gv.html}{Dr. G.A.W. \textsc{Vreeswijk}, \href{http://www.uu.nl}\textsc{UU}}  \\ % Supervisor name - remove the \href bracket to remove the link
\href{http://www.annevanrossum.com}{A.C. \textsc{van Rossum}, \href{http://www.almende.com}\textsc{Almende B.V.}} % Supervisor name - remove the \href bracket to remove the link
\end{flushright}
\end{minipage}\\[3cm]

@@

The acknowledgements and the people to thank go here, don't forget to include your project advisor\ldots
}
\TODO{Write some nice stuff here}
\clearpage % Start a new page
